Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-11 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }

@@

@@

@@

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }
\newcommand{\iotal}[1][]{\ensuremath{\iota^{\mathrm{L{#1}}}}}
\newcommand{\iotar}[1][]{\ensuremath{\iota^{\mathrm{R{#1}}}}}

@@

Recall that given a set of intervals\nb$\mathscr{I}$, we want to
know whether there is an QIVPM mapping to $\mathscr{I}$. If there
is a QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, we want
to verify whether $\bar{\mu}$ has a non-empty core. Usually, the
easiest way to prove the existence is to construct an example. As
in example~\ref{ex:three-dimensional-5-value}, constructing a QIVPM
directly is long and tedious. In contrast, a quantum probability measure\nb$\mu:\events\rightarrow\left[0,1\right]$
can be easily constructed by the Born rule. Therefore, it would be
desirable if we can construct a QIVPM\nb$\bar{\mu}$ from $\mu$,
and expect $\mu$ is in the core of $\bar{\mu}$.

Notice that the range of $\mu$ and $\bar{\mu}$ are different. If
there is a good function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$,
then a QIVPM can be easily defined by function composition\nb$\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
This gives the following definition.

@@

Although a convex pair\nb$\left(\mathscr{I},\iota\right)$ may look
exotic, the left end of $\iota$, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
is the well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,Pales2013}.
After we define\nb$\left(\mathscr{I},\iota\right)$, we are ready
to construct a QIVPM from a quantum probability measure.

@@

Although a QIVPM can be constructed by an additive pair easily, a
convex pair may not give a convex QIVPM with non-trivial finite number
of intervals. Notice a Wright-convex function is midpoint-convex or
Jensen-convex, i.e., 
\begin{equation}
\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\textrm{ ,}
\end{equation}
and a midpoint-convex function is continuous on an open interval if
we cannot use the Axiom of Choices\nb\cite{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
Therefore, for any convex QIVPM constructed by a convex pair\nb$\left(\mathscr{I},\iota\right)$,
$\mathscr{I}$ must either be $\left\{ \necess,\imposs,\unknown\right\} $
or contain infinitely many intervals.
